---
title: "Final Project Version 1.0 "
author: Jimin Wang
subtitle: R_503_final_project
---

# Project Background
The main topics: Using Geographic Weighted Regression to evaluate NYS Home Value  

> Key words: Home Value; GWR; MGWR; Sustainable Life Index; OLS

# Materials and methods

To be Continue ...

Project Composition :

* The first most important thing
* The second most important thing
* The third most important thing

<<<<<<< HEAD

Load any required packages in a code chunk (you may need to install some packages):
=======
>>>>>>> 14ae17942cbcad0e54c4847fbf253af84d059367

```{r, message=F, warning=F}
library(spgwr)
library(ggplot2)
library(tidyverse)
library(sp)
library(sf)
knitr::opts_chunk$set(cache=TRUE)  # cache the results for quick compiling
```

<<<<<<< HEAD

## Read NY state .shp basemap from file
```{r echo=FALSE}
file <- "data/map/NYS_County/Counties.shp"
NYS_shp <- sf::read_sf(file, quiet = T,  stringsAsFactors = FALSE)
plot(NYS_shp$geometry)
```


## Read csv data from file
## Read median house price value data
```{r median_house_price, echo = FALSE}
median_house_price <- read.csv("data/census_statistics/median_house_value_2014.csv")
NYS_shp_house = left_join(NYS_shp,median_house_price, by="NAME" )
median_home_value_c <- median_house_price$median.home.value /1000
=======
Load any required packages in a code chunk (you may need to install some packages):

```{r, message=F, warning=F}
library(spgwr)
library(ggplot2)
library(tidyverse)
library(sp)
library(sf)
knitr::opts_chunk$set(cache=TRUE)  # cache the results for quick compiling
>>>>>>> 14ae17942cbcad0e54c4847fbf253af84d059367
```

## visualization: Median Home Value
```{r echo=FALSE}
ggplot() + geom_sf(aes(fill = median.home.value), data = NYS_shp_house,color = "white") + scale_fill_viridis_c(option = "plasma")
```

<<<<<<< HEAD

## Read unemployment rate data
```{r unemployment, echo=FALSE}
unemployment <- read.csv("data/census_statistics/unemploymentRate_2014.csv")
NYS_shp_UERate = left_join(NYS_shp,unemployment, by="NAME" )
unemployment_rate_c <- unemployment$Unemployment.rate
```

## visualization: Unemployment Rate
```{r echo=FALSE}
ggplot() + geom_sf(aes(fill = Unemployment.rate), data = NYS_shp_UERate,color = "white") + scale_fill_viridis_c(option = "plasma")
```


## Read higher education rate data
```{r higher_education,echo=FALSE}
higher_education <- read.csv("data/census_statistics/high_education_rate_2014.csv")
NYS_shp_highEdu = left_join(NYS_shp,higher_education, by="NAME" )
higherEdu_rate_c <- higher_education$Higher.Education
```

## visualization: Percent of residents with bachelor or above degree
```{r,echo=FALSE}
ggplot() + geom_sf(aes(fill = Higher.Education), data = NYS_shp_highEdu, color = "white") + scale_fill_viridis_c(option = "plasma")
```


## Read average vehicle data
```{r vehicle_1000,echo=FALSE}
vehicle_1000<- read.csv("data/census_statistics/vehicle_ownership_2014.csv")
NYS_shp_vehicle = left_join(NYS_shp,vehicle_1000, by="NAME" )
vehicle_ave_c <- (vehicle_1000$average.vehicle1000)/1000
```

## visualization: vehicle ownership per 1000 people
```{r,echo=FALSE}
ggplot() + geom_sf(aes(fill = average.vehicle1000), data = NYS_shp_vehicle, color = "white") + scale_fill_viridis_c(option = "plasma")
```

## Read senior population rate data
```{r senior_pop_rate}
senior_pop_rate<- read.csv("data/census_statistics/senior_population_2014.csv")
NYS_shp_senior = left_join(NYS_shp,senior_pop_rate, by="NAME" )
senior_pop_c <- senior_pop_rate$Senior.Pop
```

## visualization: population over 65 percent
```{r echo=FALSE}
ggplot() + geom_sf(aes(fill =Senior.Pop), data = NYS_shp_senior, color = "white") + scale_fill_viridis_c(option = "plasma")
```

## Read tax rate data
```{r tax_rate}
tax_rate<- read.csv("data/census_statistics/property_tax_rate_2014.csv")
NYS_shp_tax = left_join(NYS_shp,tax_rate, by="NAME" )
tax_rate_c <- tax_rate$Tax
```

=======
## Read NY state .shp basemap from file
```{r echo=FALSE}
file <- "data/map/NYS_County/Counties.shp"
NYS_shp <- sf::read_sf(file, quiet = T,  stringsAsFactors = FALSE)
plot(NYS_shp$geometry)
```


## Read csv data from file
## Read median house price value data
```{r median_house_price, echo = FALSE}
median_house_price <- read.csv("data/census_statistics/median_house_value_2014.csv")
NYS_shp_house = left_join(NYS_shp,median_house_price, by="NAME" )
median_home_value_c <- median_house_price$median.home.value /1000
```

## visualization: Median Home Value
```{r echo=FALSE}
ggplot() + geom_sf(aes(fill = median.home.value), data = NYS_shp_house,color = "white") + scale_fill_viridis_c(option = "plasma")
```


## Read unemployment rate data
```{r unemployment, echo=FALSE}
unemployment <- read.csv("data/census_statistics/unemploymentRate_2014.csv")
NYS_shp_UERate = left_join(NYS_shp,unemployment, by="NAME" )
unemployment_rate_c <- unemployment$Unemployment.rate
```

## visualization: Unemployment Rate
```{r echo=FALSE}
ggplot() + geom_sf(aes(fill = Unemployment.rate), data = NYS_shp_UERate,color = "white") + scale_fill_viridis_c(option = "plasma")
```


## Read higher education rate data
```{r higher_education,echo=FALSE}
higher_education <- read.csv("data/census_statistics/high_education_rate_2014.csv")
NYS_shp_highEdu = left_join(NYS_shp,higher_education, by="NAME" )
higherEdu_rate_c <- higher_education$Higher.Education
```

## visualization: Percent of residents with bachelor or above degree
```{r,echo=FALSE}
ggplot() + geom_sf(aes(fill = Higher.Education), data = NYS_shp_highEdu, color = "white") + scale_fill_viridis_c(option = "plasma")
```


## Read average vehicle data
```{r vehicle_1000,echo=FALSE}
vehicle_1000<- read.csv("data/census_statistics/vehicle_ownership_2014.csv")
NYS_shp_vehicle = left_join(NYS_shp,vehicle_1000, by="NAME" )
vehicle_ave_c <- (vehicle_1000$average.vehicle1000)/1000
```

## visualization: vehicle ownership per 1000 people
```{r,echo=FALSE}
ggplot() + geom_sf(aes(fill = average.vehicle1000), data = NYS_shp_vehicle, color = "white") + scale_fill_viridis_c(option = "plasma")
```

## Read senior population rate data
```{r senior_pop_rate}
senior_pop_rate<- read.csv("data/census_statistics/senior_population_2014.csv")
NYS_shp_senior = left_join(NYS_shp,senior_pop_rate, by="NAME" )
senior_pop_c <- senior_pop_rate$Senior.Pop
```

## visualization: population over 65 percent
```{r echo=FALSE}
ggplot() + geom_sf(aes(fill =Senior.Pop), data = NYS_shp_senior, color = "white") + scale_fill_viridis_c(option = "plasma")
```

## Read tax rate data
```{r tax_rate}
tax_rate<- read.csv("data/census_statistics/property_tax_rate_2014.csv")
NYS_shp_tax = left_join(NYS_shp,tax_rate, by="NAME" )
tax_rate_c <- tax_rate$Tax
```

>>>>>>> 14ae17942cbcad0e54c4847fbf253af84d059367
## visualization: property tax rate
```{r echo=FALSE}
ggplot() + geom_sf(aes(fill = Tax), data = NYS_shp_tax, color = "white") + scale_fill_viridis_c(option = "plasma")
```


## First Model: OLS -- Multivariat Linear Regression
```{r ols-model, echo=FALSE}
dataFrame = data.frame(median_home_value_c,unemployment_rate_c,senior_pop_c,vehicle_ave_c,higherEdu_rate_c,tax_rate_c)
model1 <- lm(formula = median_home_value_c ~ unemployment_rate_c+senior_pop_c+vehicle_ave_c+higherEdu_rate_c+tax_rate_c)
summary(model1)
```

# Conclusions

What have you learned?  Are there any broader implications?

# References

