---
title: "GWR Spatial Corelation in NYS Housing Price"
Author: Jimin Wang
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

Below are codes to read all spatial data and run the GWR model

## load necesssary packages

```{r eval = FALSE}
library(spgwr)
library(ggplot2)
library(tidyverse)
library(sp)
library(sf)
```

## Read NY state .shp basemap from file
```{r echo=FALSE}
file <- "F:/GEO/503DataScience/final_project_materials/data/map/NYS_County/Counties.shp"
NYS_shp <- sf::read_sf(file, quiet = T,  stringsAsFactors = FALSE)
plot(NYS_shp$geometry)
```


## Read csv data from file
## Read median house price value data
```{r csvData, echo = FALSE}
median_house_price <- read.csv("F:/GEO/503DataScience/final_project_materials/data/median_house_value_2014.csv")
## NYS_shp_house = left_join(NYS_shp,median_house_price, by="NAME" )
median_home_value_c <- median_house_price$median.home.value /1000
```

## visualization: Median Home Value
```{r echo=FALSE}
ggplot() + geom_sf(aes(fill = median.home.value), data = NYS_shp_house,color = "white") + scale_fill_viridis_c(option = "plasma")
```


## Read unemployment rate data
```{r csvData, echo=FALSE}
unemployment <- read.csv("F:/GEO/503DataScience/final_project_materials/data/unemploymentRate_2014.csv")
## NYS_shp_UERate = left_join(NYS_shp,unemployment, by="NAME" )
unemployment_rate_c <- unemployment$Unemployment.rate
```

## visualization: Unemployment Rate
```{r echo=FALSE}
ggplot() + geom_sf(aes(fill = Unemployment.rate), data = NYS_shp_UERate,color = "white") + scale_fill_viridis_c(option = "plasma")
```


## Read higher education rate data
```{r csvData,echo=FALSE}
higher_education <- read.csv("F:/GEO/503DataScience/final_project_materials/data/high_education_rate_2014.csv")
## NYS_shp_highEdu = left_join(NYS_shp,higher_education, by="NAME" )
higherEdu_rate_c <- higher_education$Higher.Education
```

## visualization: Percent of residents with bachelor or above degree
```{r,echo=FALSE}
ggplot() + geom_sf(aes(fill = Higher.Education), data = NYS_shp_highEdu, color = "white") + scale_fill_viridis_c(option = "plasma")
```


## Read average vehicle data
```{r csvData,echo=FALSE}
vehicle_1000<- read.csv("F:/GEO/503DataScience/final_project_materials/data/vehicle_ownership_2014.csv")
## NYS_shp_vehicle = left_join(NYS_shp,vehicle_1000, by="NAME" )
vehicle_ave_c <- (vehicle_1000$average.vehicle1000)/1000
```

## visualization: vehicle ownership per 1000 people
```{r,echo=FALSE}
ggplot() + geom_sf(aes(fill = average.vehicle1000), data = NYS_shp_vehicle, color = "white") + scale_fill_viridis_c(option = "plasma")
```

## Read senior population rate data
```{r csvData}
senior_pop_rate<- read.csv("F:/GEO/503DataScience/final_project_materials/data/senior_population_2014.csv")
## NYS_shp_senior = left_join(NYS_shp,senior_pop_rate, by="NAME" )
senior_pop_c <- senior_pop_rate$Senior.Pop
```

## visualization: population over 65 percent
```{r ols-model}
ggplot() + geom_sf(aes(fill =Senior.Pop), data = NYS_shp_senior, color = "white") + scale_fill_viridis_c(option = "plasma")
```

## Read tax rate data
```{r csvData}
tax_rate<- read.csv("F:/GEO/503DataScience/final_project_materials/data/property_tax_rate_2014.csv")
## NYS_shp_tax = left_join(NYS_shp,tax_rate, by="NAME" )
tax_rate_c <- tax_rate$Tax
```

## visualization: property tax rate
```{r ols-model}
ggplot() + geom_sf(aes(fill = Tax), data = NYS_shp_tax, color = "white") + scale_fill_viridis_c(option = "plasma")
```


## First Model: OLS -- Multivariat Linear Regression
```{r ols-model, echo=FALSE}
dataFrame = data.frame(median_home_value_c,unemployment_rate_c,senior_pop_c,vehicle_ave_c,higherEdu_rate_c,tax_rate_c)
model1 <- lm(formula = median_home_value_c ~ unemployment_rate_c+senior_pop_c+vehicle_ave_c+higherEdu_rate_c+tax_rate_c,dataFrame)
summary(model1)
```

## Second Model: GWR -- Geographic Weighted Regression
```{r gwr-model_data_prepare, echo=FALSE}
coord = st_centroid(NYS_shp$geometry)
coords_frame <- unlist(st_geometry(coord)) %>% 
  matrix(ncol=2,byrow=TRUE) %>% 
  as_tibble() %>% 
  setNames(c("x","y"))

dataFrame_gwr = data.frame(dataFrame,coords_frame)
```

## load GWR model
```{r gwr-model}
GWRbandwidth <- gwr.sel(median_home_value_c ~ unemployment_rate_c+senior_pop_c+vehicle_ave_c+higherEdu_rate_c+tax_rate_c, data=dataFrame_gwr, coords=cbind(dataFrame_gwr$x,dataFrame_gwr$y),adapt=T) 
gwr.model = gwr(median_home_value_c ~ unemployment_rate_c+senior_pop_c+vehicle_ave_c+higherEdu_rate_c+tax_rate_c, data=dataFrame_gwr, coords=cbind(dataFrame_gwr$x,dataFrame_gwr$y), adapt=GWRbandwidth, hatmatrix=TRUE, se.fit=TRUE) 
#print the results of the model
gwr.model
```
